% Content added in a chronological order

\section{\underline{Work Experience}}

\large{\textbf{Master Thesis Student}}
\hfill
%\hspace{2.9 in}
\masterarbeitdate\\
\large{\emph{Rheinmetall Technology Centre - New Technologies, Rheinmetall AG, Neuss, Germany}}\\
\large{\textbf{Distributed Data-Fusion and Control over a network of Unmanned Aerial Vehicles}}
%\masterarbeitBetreuer
\begin{itemize}
    \item Development of a simulation model of an integrated flight control system for a single UAV, including a flight controller, 6 degree-of-freedom UAV dynamic model, IMU, Magnetometer, Barometer and GPS sensor models and an Extended Kalman Filter for attitude estimation.
    %\item Implementation of inertial strapdown algorithms to propogate the attitude in time and compliment the attitude filter.
    \item Design of an attitude estimation filter based on attitude error rotation vector dynamics.
    \item Development of a localization algorithm for a network of GPS-denied UAVs using Ultra-wideband (UWB) sensors.
\end{itemize}

\vspace{0.1 in}

\large{\textbf{Werkstudent (Working Student)}}
\hfill
%\hspace{2.9 in}
\rheinmetalldate\\
\large{\emph{Rheinmetall Technology Centre - New Technologies, Rheinmetall AG, Neuss, Germany}}
\begin{itemize}
%\item\large{Involved in a project about a novel electrostatic synchronous actuator for flexible exoskeletons}
\item\large{Development of a mathematical model for the force analysis of a flexible electrostatic synchronous actuator based on the concept of \emph{Method of Moments}, a discretization technique for electric fields.}
%\item\large{Validation of the simulation models against real-time testing of the actuator prototype}
\item\large{Maintainance of the developed mathematical model code-base, making use of software engineering principles like object orientation, version control and comprehensive code documentation}
\end{itemize}

\vspace{0.1 in}

\large{\textbf{Project Assistant}}
\hfill
%\hspace{4.1 in}
\minithesisdate\\
\emph{\large{Institut für Getriebetechnik, Maschinendynamik und Robotik, RWTH Aachen}}
\begin{itemize}
\item \large{Scripting Multi-Body simulation models of a standard mountain bike in Simpack using the \emph{Semi-Analytical Approach} where the multibody model partly depends on real-time sensing of loads on the actual bike.}
\item\large{Setting up co-simulation between Simpack and Simulink in a closed loop simulation for stabilizing the multibody model of the bike excited by the measured loads.}
%\item\large{Testing various linear control techniques in order to achieve disturbance rejection}.
\item\large{The work in this project culminated in a mini-thesis worth 9 ECTS, which can be accessed \href{https://github.com/average-engineer/MiniThesis_IGMR/blob/master/Thesis.pdf}{\large{\textit{here}}}.}
\end{itemize}

\vspace{0.1 in}

\large{\textbf{Research Assistant}}
\hfill
%\hspace{4.1 in}
\drdodate\\
\emph{\large{Thapar Institute of Engineering and Technology, Patiala, India}}
%\textbf{Dynamic Modelling and Control Design of Augmentative Lower Extremity Exoskeleton}
\begin{itemize}
\item \large{Dynamic modeling of a strength augmentation exoskeleton designed by \emph{Defence Bio-Engineering and Electro-Medical Laboratory} (DEBEL), a branch of \emph{Defence Research and Development Organization} (DRDO), India}
\item\large{Modeling of Human and Lower Extremity Exoskeleton in the form of a coupled multi-body system with the human as leader and the exoskeleton as follower.}
\item\large{Development of a Computed Torque Control algorithm for strength augmentation.}
\item\large{Various sections of the work done for this project are being submitted in various journals and conferences related to Biomechanics and Multi-Body Dynamics, and all published work can be referred from \emph{Conference Presentations and Publications} section.}
\end{itemize}

\vspace{0.1 in}

\large{\textbf{Teaching Assistant}}
\hfill
%\hspace{4.1 in}
\thapardate\\
\emph{\large{Thapar Institute of Engineering and Technology, Patiala, India}}
\begin{itemize}
	\item Teaching Assistant for the graduate level course \emph{Modern Control of Dynamic Systems}, which covers basic and advanced topics in linear systems theory like state-space representations, canonical forms, controller and observer design using pole-placement, and some concepts of optimal control theory.
	\item Helped set mid-term examinations and quizzes, and grade them as part of assitantship duties.
\end{itemize}

